Molecular Analysis

### 2023-06-22 analysis/epi_analysis.Rmd
minor update to result plots

# number of cases by week
cases_by_week_pl <- epi_data %>%
  mutate(week = isoweek(date)) %>%
  filter(week != 6) %>%
  group_by(class, week) %>%
  summarize(cases = sum(new_cases),
            aircleaner = first(aircleaner)) %>%
  ungroup() %>%
  ggplot(aes(x = factor(week), y = cases, fill = aircleaner)) +
  geom_bar_pattern(stat = "identity", aes(pattern_angle = class), pattern = "stripe",
                   pattern_fill = "white", pattern_color = NA, color = "black", pattern_density = 0.25, pattern_spacing = 0.05) +
  labs(x = "Study week", y = "Number of cases", fill = "Air cleaner", pattern_angle = "Class", title = "a") +
  scale_fill_manual(values = wes_palette("Royal1")) +
  scale_x_discrete(breaks = c(1:5, 7:10)) +
  scale_y_continuous(expand = expansion(mult = c(0, 0.05))) +
  scale_pattern_angle_discrete(range = c(-45, 45)) +
  theme_custom() +
  theme(legend.position = c(0.13, 0.8),
        legend.key.width = unit(0.5, "cm"),
        legend.key.height = unit(0.3, "cm"),
        plot.title.position = "plot") +
  guides(fill = guide_legend(nrow = 1),
         pattern_angle = guide_legend(nrow = 1))

save_plot(cases_by_week_pl,
          pdf_file = "../results/epi-data/cases_by_week.pdf",
          eps_file = "../results/epi-data/cases_by_week.eps",
          w = 12, h = 8) 
```

>>>>

# number of cases by week
cases_by_week_pl <- epi_data %>%
  mutate(week = isoweek(date)) %>%
  filter(week != 6) %>%
  group_by(class, week) %>%
  summarize(cases = sum(new_cases),
            aircleaner = first(aircleaner)) %>%
  ungroup() %>%
  mutate(aircleaner = factor(aircleaner, levels = c("Yes", "No")),
         class = factor(class, levels = c("A", "B"))) %>%
  arrange(class, aircleaner) %>%
  ggplot(aes(x = factor(week), y = cases, fill = aircleaner, pattern = class)) +
  geom_bar_pattern(stat = "identity", color = "black", pattern_fill = "white", pattern_angle = 45,
                   pattern_density = 0.25, pattern_spacing = 0.05) +
  labs(x = "Study week", y = "Number of cases", fill = "Air cleaner", pattern = "Class", title = "a") +
  scale_fill_manual(values = rev(wes_palette("Royal1")[1:2])) +
  scale_x_discrete(breaks = c(1:5, 7:10)) +
  scale_y_continuous(expand = expansion(mult = c(0, 0.05))) +
  scale_pattern_manual(values = c(A = "stripe", B = "none")) +
  theme_custom() +
  theme(legend.position = c(0.13, 0.8),
        legend.key.width = unit(0.5, "cm"),
        legend.key.height = unit(0.3, "cm"),
        plot.title.position = "plot") +
  guides(fill = guide_legend(nrow = 1, override.aes = list(pattern = "none", order = 2)),
         pattern = guide_legend(nrow = 1, override.aes = list(fill = "white"), order = 1))

save_plot(cases_by_week_pl,
          pdf_file = "../results/epi-data/cases_by_week.pdf",
          eps_file = "../results/epi-data/cases_by_week.eps",
          w = 16, h = 8) 
```

### 2023-06-22 analysis/mol_analysis.Rmd
minor update to result plots

pos_week_pl <- ggplot(mapping = aes(x = week, y = n, fill = variable)) +
  geom_bar(data = df_pos, stat = "identity") +
  geom_text(data = subset(df_pos, n > 0), mapping = aes(label = n), 
            size = 8 / cm(1), position = position_stack(vjust = 0.5), color = "white") +
  facet_wrap(~ class) +
  scale_fill_manual(values = wes_palette("IsleofDogs1")) +
  scale_y_continuous(expand = expansion(add = c(0,1))) +
  scale_x_continuous(breaks = seq(1, 7, 1)) +
  labs(y = "Number of positive samples", x = "Study week", fill = "Virus", title = "c") +
  theme_custom() +
  theme(panel.grid = element_blank(),
        legend.position = "none") +
  guides(fill = guide_legend(nrow = 1))
pos_week_pl
```

```{r}
# positive samples by study condition
df_pos_stud <- df_pos %>%
  group_by(aircleaner, variable) %>%
  summarize(n = sum(n)) %>%
  ungroup()
pos_cond_pl <- ggplot(mapping = aes(x = aircleaner, y = n, fill = variable)) +
  geom_bar(data = df_pos_stud, stat = "identity", position = "stack") +
  geom_text(data = subset(df_pos_stud, n != 0), mapping = aes(label = n), 
            size = 8 / cm(1), position = position_stack(vjust = 0.5), color = "white") +
  scale_fill_manual(values = wes_palette("IsleofDogs1")) +
  scale_y_continuous(expand = c(0,0)) +
  labs(y = "Number of positive samples", x = "Air cleaner", fill = "Virus", title = "b") +
  theme_custom() +
  theme(panel.grid = element_blank(),
        legend.position = "bottom") +
  guides(fill = guide_legend(nrow = 1))
pos_cond_pl
```

@@

pos_tot_pl <- df_pos_tot %>%
  ggplot(aes(x = variable, y = n, fill = variable)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = n, y = n + 1), size = 8 / cm(1)) +
  scale_fill_manual(values = wes_palette("IsleofDogs1")) +
  scale_y_continuous(expand = expansion(add = c(0,1))) +
  labs(y = "Number of positive samples", x = "Air cleaner", fill = "Virus", title = "a") +
  theme_custom() +
  theme(panel.grid = element_blank(),
        legend.position = "bottom") +
  guides(fill = guide_legend(nrow = 1))
pos_tot_pl
```

>>>>

pos_week_pl <- ggplot(mapping = aes(x = week, y = n, fill = variable)) +
  geom_bar(data = df_pos, stat = "identity") +
  geom_text(data = subset(df_pos, n > 0), mapping = aes(label = n), 
            size = 8 / cm(1), position = position_stack(vjust = 0.5), color = "white") +
  facet_wrap(~ class) +
  scale_fill_manual(values = wes_palette("IsleofDogs1")) +
  scale_y_continuous(expand = expansion(add = c(0,1))) +
  scale_x_continuous(breaks = seq(1, 7, 1)) +
  labs(y = "Number of positive samples", x = "Study week", fill = "Pathogen", title = "c") +
  theme_custom() +
  theme(panel.grid = element_blank(),
        legend.position = "none") +
  guides(fill = guide_legend(nrow = 1))
pos_week_pl
```

```{r}
# positive samples by study condition
df_pos_stud <- df_pos %>%
  group_by(aircleaner, variable) %>%
  summarize(n = sum(n)) %>%
  ungroup()
pos_cond_pl <- ggplot(mapping = aes(x = aircleaner, y = n, fill = variable)) +
  geom_bar(data = df_pos_stud, stat = "identity", position = "stack") +
  geom_text(data = subset(df_pos_stud, n != 0), mapping = aes(label = n), 
            size = 8 / cm(1), position = position_stack(vjust = 0.5), color = "white") +
  scale_fill_manual(values = wes_palette("IsleofDogs1")) +
  scale_y_continuous(expand = c(0,0)) +
  labs(y = "Number of positive samples", x = "Air cleaner", fill = "Pathogen", title = "b") +
  theme_custom() +
  theme(panel.grid = element_blank(),
        legend.position = "bottom") +
  guides(fill = guide_legend(nrow = 1))
pos_cond_pl
```

@@

pos_tot_pl <- df_pos_tot %>%
  ggplot(aes(x = variable, y = n, fill = variable)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = n, y = n + 1), size = 8 / cm(1)) +
  scale_fill_manual(values = wes_palette("IsleofDogs1")) +
  scale_y_continuous(expand = expansion(add = c(0,1))) +
  labs(y = "Number of positive samples", x = "Pathogen", fill = "Pathogen", title = "a") +
  theme_custom() +
  theme(panel.grid = element_blank(),
        legend.position = "bottom") +
  guides(fill = guide_legend(nrow = 1))
pos_tot_pl
```
